---
title: "Spider traits"
author: "Caio Graco-Roza"
date: "3/22/2021"
output:
  pdf_document: default
  html_document: default
editor_options:
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message=FALSE,
                      warning=FALSE)

pacman::p_load(tidyverse, gawdis,ggpointdensity,patchwork,readxl, ggtext, ggnewscale,summarytools, ggdist, formatR)

data  <- read_excel("DATABASE_CAVE_TRAITS.xlsx", na = "NA")

```

This code aims to provide code for making a super amazing figure of cave spiders functional diversity. Any comments on what to change can be written here and sent back to me.

# Data wrangling

```{r trait transformation}
#Select traits that will be used

trait <-
  data %>%
  select(
    Pigment,
    Eyeless,
    Eyes_regression,
    Eye_reduction_ratio,
    AME,
    ALE,
    PME,
    PLE,
    AME_type,
    # All the eye variables
    ends_with(c("_web", "_hunter")),
    Food_specialist,
    Dispersal,
    Verticality,
    Body_length_avg,
    Sexual_Size_Dimorphism,
    Leg_elongation,
    Femur_elongation,
    Profile_flattening,
    Prosoma_shape,
    Fang_length_avg
  )  %>%
  mutate_at(vars("AME", "ALE", "PME", "PLE"), as.numeric) %>%
  mutate_at("AME_type", as.factor) %>%
  mutate_at("Pigment", ordered, levels = rev(c(
    "Depigmented", "Partly", "Variable", "Fully"
  ))) %>%
  mutate_at(vars(-c("Pigment", "Verticality", 'AME_type')), ~ as.numeric(as.character(.))) %>%
  mutate_at(vars(Pigment, Verticality), as.factor) %>%
  mutate_at(
    vars(
      Prosoma_shape,
      Profile_flattening,
      Femur_elongation,
      Body_length_avg,
      Fang_length_avg
    ),
    ~ log1p(.)
  ) %>%
  mutate(web_strategy = names(data[, 70:72])[max.col(data[, 70:72])]) %>%
  select(-c("Capture_web", "Sensing_web", "No_web")) %>%
  mutate_if(is.character, as.factor)

```

# Data exploration

General summary of the data in a table form

```{r, results = 'asis'}
print(dfSummary(trait, style='grid'), method = "render")
```

Checking missing data

```{r Missing data}
# Missing data 
Amelia::missmap(trait)
```

Removing empty traits and updating the string for continuous

```{r empty traits}
trait_m <- trait %>% select (-c("Profile_flattening", "Fang_length_avg")) #remove empty traits


continuous <- c(4:8, 19:20, 22:23)  #vector of columns with continuous traits

# Standardize continuous traits
trait_m <- BAT::standard(data.frame(trait_m), method = "standard", convert = continuous) 

#Check outliers
par(mfrow = c(3, 3))
for (i in continuous) {
  dotchart(sort(trait_m[, i]), main = colnames(trait_m)[i])
}
```

```{r Collinearity}
# Check Collinearity
psych::pairs.panels(trait_m[,colnames(trait_m[continuous])])
```

```{r colour pallete, message=FALSE, warning=FALSE}
myCol<-viridis::viridis(n=6, option="B") #Make Color palette 
pie(seq_along(myCol),myCol,col= myCol)
```

# Set the main theme for plots

```{r theme settings}
theme_set(theme_bw())
theme_update(
  legend.position = "none", #No legend
  plot.background = element_blank(), #No background
  panel.grid = element_blank(), #No gridlines
  axis.text.x = element_text(size = 10, colour = "black") #Font 10 for x axis
)
```

# Figure 2

```{r figure 2 build}

ALE <- data %>%
  select(Cave_deep, ALE) %>%  #Select the variables to be plotted
  mutate_at("Cave_deep",as.factor) %>% #Conver binary to factor
  mutate_at("ALE",as.numeric) %>% #Convert trait to numeric
  na.exclude() %>% #remove NAs from ALE
  ggplot(aes(x= Cave_deep, y=ALE), fill = myCol[3]) +
    ggdist::stat_halfeye(aes(fill =Cave_deep),
    width = .3,    ## adjust height
    justification = -.4,    ## move geom to the right
    .width = 0,    ## remove slab interval
    point_colour = NA,
    normalize="panels"
  ) +
    geom_boxplot(aes(colour = Cave_deep),
    width = .15, 
    outlier.color = NA,  ## remove outliers
  ) +
    gghalves::geom_half_point(
    aes(colour = Cave_deep),
    side = "l",    ## draw jitter on the left
    range_scale = .4,    ## control range of jitter
    size=.5,
    alpha = .3    ## add some transparency
  ) +
  scale_x_discrete(labels=c("No","Yes"))+ # zeros become No, ones become Yes 
  scale_fill_manual(values=c("grey20",myCol[3]))+ #set colours to points
  scale_colour_manual(values=c("grey20",myCol[3]))+ #set colours to density
  ylab("")+
  xlab("Occurring deep inside caves\n  (dark zone)")+
  ggtitle("Anterior Lateral Eyes")+
  coord_cartesian(xlim=c(1.2,NA))


AME <- data %>%
  select(Cave_deep, AME) %>% 
  mutate_at("Cave_deep",as.factor) %>%
  mutate_at("AME",as.numeric) %>%
  na.exclude() %>%
  ggplot(aes(x=Cave_deep, y=AME)) +
    ggdist::stat_halfeye(aes(fill =Cave_deep),
    width = .3,    ## adjust height
    justification = -.4,    ## move geom to the right
    .width = 0,    ## remove slab interval
    point_colour = NA,
    normalize="panels"
  ) +
    geom_boxplot(aes(colour = Cave_deep),
    width = .15, 
    outlier.color = NA,  ## remove outliers
  ) +
    gghalves::geom_half_point(
    aes(colour = Cave_deep),
    side = "l",    ## draw jitter on the left
    range_scale = .4,    ## control range of jitter
    size=.5,
    alpha = .3    ## add some transparency
  ) +
  scale_x_discrete(labels=c("No","Yes"))+
  scale_fill_manual(values=c("grey20",myCol[3]))+
  scale_colour_manual(values=c("grey20",myCol[3]))+
  ylab("")+
  xlab("")+
  ggtitle("Anterior Median Eyes")+
  coord_cartesian(xlim=c(1.2,NA))


PLE <- data %>%
  select(Cave_deep, PLE) %>% 
  mutate_at("Cave_deep",as.factor) %>%
  mutate_at("PLE",as.numeric) %>%
  na.exclude() %>%
  ggplot(aes(x= Cave_deep, y=PLE), fill = myCol[3]) +
    ggdist::stat_halfeye(aes(fill =Cave_deep, colour=Cave_deep),
    width = .3,    ## adjust height
    justification = -.4,    ## move geom to the right
    .width = 0,    ## remove slab interval
    point_colour = NA,
    normalize="panels"
  ) +
    geom_boxplot(aes(colour = Cave_deep),
    width = .15, 
    outlier.color = NA,  ## remove outliers
  ) +
    gghalves::geom_half_point(
    aes(colour = Cave_deep),
    side = "l",    ## draw jitter on the left
    range_scale = .4,    ## control range of jitter
    size=.5,
    alpha = .3    ## add some transparency
  ) +
  scale_x_discrete(labels=c("No","Yes"))+
  scale_fill_manual(values=c("grey20",myCol[3]))+
  scale_colour_manual(values=c("grey20",myCol[3]))+
  ylab("")+
  xlab("Occurring deep inside caves\n  (dark zone)")+
  ggtitle("Posterior Lateral Eyes")+
  coord_cartesian(xlim=c(1.2,NA))


PME <- data %>%
  select(Cave_deep, PME) %>% 
  mutate_at("Cave_deep",as.factor) %>%
  mutate_at("PME",as.numeric) %>%
  na.exclude() %>%
  ggplot(aes(x=Cave_deep, y=PME)) +
    ggdist::stat_halfeye(aes(fill =Cave_deep),
    width = .3,    ## adjust height
    justification = -.4,    ## move geom to the right
    .width = 0,    ## remove slab interval
    point_colour = NA,
    normalize="panels"
  ) +
    geom_boxplot(aes(colour = Cave_deep),
    width = .15, 
    outlier.color = NA,  ## remove outliers
  ) +
    gghalves::geom_half_point(
    aes(colour = Cave_deep),
    side = "l",    ## draw jitter on the left
    range_scale = .4,    ## control range of jitter
    size=.5,
    alpha = .3    ## add some transparency
  ) +
  scale_x_discrete(labels=c("No","Yes"))+
  scale_fill_manual(values=c("grey20",myCol[3]))+
  scale_colour_manual(values=c("grey20",myCol[3]))+
  ylab("")+
  xlab("")+
  ggtitle("Posterior Median Eyes")+
  coord_cartesian(xlim=c(1.2,NA))
    
Body_length <- data %>%
  select(Cave_deep, Body_length_avg) %>% 
  mutate_at("Cave_deep",as.factor) %>%
  mutate_at("Body_length_avg",as.numeric) %>%
  na.exclude() %>%
  ggplot(aes(x= Cave_deep, y=Body_length_avg), fill = myCol[3]) +
    ggdist::stat_halfeye(aes(fill =Cave_deep),
    width = .3,    ## adjust height
    justification = -.4,    ## move geom to the right
    .width = 0,    ## remove slab interval
    point_colour = NA,
    normalize="panels"
  ) +
    geom_boxplot(aes(colour = Cave_deep),
    width = .15, 
    outlier.color = NA,  ## remove outliers
  ) +
    gghalves::geom_half_point(
    aes(colour = Cave_deep),
    side = "l",    ## draw jitter on the left
    range_scale = .4,    ## control range of jitter
    size=.5,
    alpha = .3    ## add some transparency
  ) +
  scale_x_discrete(labels=c("No","Yes"))+
  scale_fill_manual(values=c("grey20",myCol[3]))+
  scale_colour_manual(values=c("grey20",myCol[3]))+
  ylab("")+
  xlab("")+
  ggtitle("Body length")+
  coord_cartesian(xlim=c(1.2,NA))

Femur_elongation <- data %>%
  select(Cave_deep, Femur_elongation) %>% 
  mutate_at("Cave_deep",as.factor) %>%
  mutate_at("Femur_elongation",as.numeric) %>%
  na.exclude() %>%
  ggplot(aes(x= Cave_deep, y=Femur_elongation), fill = myCol[3]) +
    ggdist::stat_halfeye(aes(fill =Cave_deep, colour=Cave_deep),
      width = .3,    ## adjust height
    justification = -.4,    ## move geom to the right
    .width = 0,    ## remove slab interval
    point_colour = NA,
    normalize="panels"
  ) +
    geom_boxplot(aes(colour = Cave_deep),
    width = .15, 
    outlier.color = NA,  ## remove outliers
  ) +
    gghalves::geom_half_point(
    aes(colour = Cave_deep),
    side = "l",    ## draw jitter on the left
    range_scale = .4,    ## control range of jitter
    size=.5,
    alpha = .3    ## add some transparency
  ) +
  scale_x_discrete(labels=c("No","Yes"))+
  scale_fill_manual(values=c("grey20",myCol[3]))+
  scale_colour_manual(values=c("grey20",myCol[3]))+
  ylab("")+
  xlab("Occurring deep inside caves\n  (dark zone)")+
  ggtitle("Femur elongation")+
  coord_cartesian(xlim=c(1.2,NA))

```

```{r Figure 2 ,fig.align='center', fig.width=6,fig.height=4}

Figure_2 <- Body_length+AME+PME+Femur_elongation+ALE+PLE + plot_layout(ncol=3, guides="collect") +  plot_annotation(tag_levels = 'A') &
  theme(plot.tag = element_text(size = 14, face = "bold"), #Tag will be size 14
        legend.position="none", #Show no legend
        axis.text.y = element_text(size=12), #all axis texts will be size 12
        axis.text.x = element_text(size=12), #all axis texts will be size 12
        axis.title.x = element_text(size=14)) # x axis title will be size 14
```

```{r, echo=FALSE}
ggsave(plot=Figure_2, filename ="Figures/Figure_2.pdf", height = 8, width=12, device=cairo_pdf)

knitr::include_graphics("Figures/Figure_2.pdf")
```

# Figure 3

```{r figure 3 build}
ALE_family <- data %>%
  select(Family, ALE, Ecological_classification) %>% #select variables to be plotted
  filter(
    Family == "Linyphiidae" |
      Family == "Agelenidae" |
      Family == "Nesticidae" |
      Family == "Leptonetidae" | Family == "Dysderidae"
  ) %>% #only some families 
  mutate_at("ALE", as.numeric) %>% #convert trait to numeric
  mutate_at("Ecological_classification", as.factor) %>% # Troglobiont and Trogophile as factors 
  na.exclude() %>% #remove NAs from the table 
  group_by(Family, Ecological_classification) %>% 
  filter(n() >= 2) %>% #Remove Families that have less than 2 species per category 
  ungroup() %>%
  ggplot(
    aes(
      x = Family,
      y = ALE,
      fill = Ecological_classification,
      colour = Ecological_classification
    )
  ) +
  stat_slab(alpha = .3, colour = NA) + #plot the density
  stat_pointinterval(position = position_dodge(width = .5, preserve = "single")) + #plot the point interval
  scale_fill_manual(values = c("grey20", myCol[3])) +
  scale_colour_manual(values = c("grey20", myCol[3])) +
  ylab("") +
  xlab("") +
  ggtitle("Anterior Lateral Eyes") +
  coord_cartesian(xlim = c(1.2, NA)) +
  theme(axis.text.x = element_text(
    angle = 30,
    vjust = 1,
    hjust = 1
  ),
  legend.position = "bottom")

AME_family <- data %>%
  select(Family, AME, Ecological_classification) %>%
  filter(
    Family == "Linyphiidae" |
      Family == "Agelenidae" |
      Family == "Nesticidae" |
      Family == "Leptonetidae" | Family == "Dysderidae"
  ) %>%
  mutate_at("Ecological_classification", as.factor) %>%
  mutate_at("Family", as.factor) %>%
  mutate_at("AME", as.numeric) %>%
  na.exclude() %>% #remove NAs
  group_by(Family, Ecological_classification) %>%
  filter(n() >= 2) %>%
  ungroup() %>%
  mutate(AME = ifelse(.$Family == "Dysderidae" |
                        .$Family == "Leptonetidae", NA, AME)) %>%
  na.exclude() %>% #remove NAs here will remove the families Dysderidae en Leptonetidae from the plot
  ggplot(
    aes(
      x = Family,
      y = AME,
      fill = Ecological_classification,
      colour = Ecological_classification
    )
  ) +
  stat_slab(alpha = .3, colour = NA) + #plot the density
  stat_pointinterval(position = position_dodge(width = .5, preserve = "single")) + #plot the point interval
  scale_fill_manual(values = c("grey20", myCol[3])) +
  scale_colour_manual(values = c("grey20", myCol[3])) +
  scale_x_discrete(
    drop = FALSE, #ensure that plot shows all families even the ones without values 
    labels = c(
      "Agelenidae",
      "Dysderidae",
      "Leptonetidae",
      "Linyphidae",
      "Nesticidae"
    )
  ) +
  ylab("") +
  xlab("") +
  ggtitle("Anterior Median Eyes") +
  coord_cartesian(xlim = c(1.2, NA)) +
  theme(axis.text.x = element_text(
    angle = 30,
    vjust = 1,
    hjust = 1
  ),
  legend.position = "bottom")
    

PLE_family <- data %>%
  select(Family, PLE, Ecological_classification) %>%
  filter(
    Family == "Linyphiidae" |
      Family == "Agelenidae" |
      Family == "Nesticidae" |
      Family == "Leptonetidae" | Family == "Dysderidae"
  ) %>%
  mutate_at("Ecological_classification", as.factor) %>%
  mutate_at("PLE", as.numeric) %>%
  na.exclude() %>%
  group_by(Family, Ecological_classification) %>%
  filter(n() >= 2) %>%
  ungroup() %>%
  ggplot(
    aes(
      x = Family,
      y = PLE,
      fill = Ecological_classification,
      colour = Ecological_classification
    )
  ) +
  stat_slab(alpha = .3, colour = NA) + #plot the density
  stat_pointinterval(position = position_dodge(width = .5, preserve = "single")) + #plot the interval
  scale_fill_manual(values = c("grey20", myCol[3])) +
  scale_colour_manual(values = c("grey20", myCol[3])) +
  ylab("") +
  xlab("") +
  ggtitle("Posterior Lateral Eyes") +
  coord_cartesian(xlim = c(1.2, NA)) +
  theme(axis.text.x = element_text(
    angle = 30,
    vjust = 1,
    hjust = 1
  ),
  legend.position = "bottom")

PME_family <- data %>%
  select(Family, PME, Ecological_classification) %>%
  filter(
    Family == "Linyphiidae" |
      Family == "Agelenidae" |
      Family == "Nesticidae" |
      Family == "Leptonetidae" | Family == "Dysderidae"
  ) %>%
  mutate_at("Ecological_classification", as.factor) %>%
  mutate_at("PME", as.numeric) %>%
  na.exclude() %>%
  group_by(Family, Ecological_classification) %>%
  filter(n() >= 2) %>%
  ungroup() %>%
  ggplot(
    aes(
      x = Family,
      y = PME,
      fill = Ecological_classification,
      colour = Ecological_classification
    )
  ) +
  stat_slab(alpha = .3, colour = NA) + #plot the density
  stat_pointinterval(position = position_dodge(width = .5, preserve = "single")) + #plot the interval
  scale_fill_manual(values = c("grey20", myCol[3])) +
  scale_colour_manual(values = c("grey20", myCol[3])) +
  ylab("") +
  xlab("") +
  ggtitle("Posterior Median Eyes") +
  coord_cartesian(xlim = c(1.2, NA)) +
  theme(axis.text.x = element_text(
    angle = 30,
    vjust = 1,
    hjust = 1
  ),
  legend.position = "bottom")
    
Body_length_family <- data %>%
  select(Family, Body_length_avg, Ecological_classification) %>%
  filter(
    Family == "Linyphiidae" |
      Family == "Agelenidae" |
      Family == "Nesticidae" |
      Family == "Leptonetidae" | Family == "Dysderidae"
  ) %>%
  mutate_at("Ecological_classification", as.factor) %>%  mutate_at("Body_length_avg", as.numeric) %>%
  na.exclude() %>%
  group_by(Family, Ecological_classification) %>%
  filter(n() >= 2) %>%
  ungroup() %>%
  ggplot(
    aes(
      x = Family,
      y = Body_length_avg,
      fill = Ecological_classification,
      colour = Ecological_classification
    )
  ) +
  stat_slab(alpha = .3, colour = NA) +
  stat_pointinterval(position = position_dodge(width = .5, preserve = "single")) +
  scale_fill_manual(values = c("grey20", myCol[3])) +
  scale_colour_manual(values = c("grey20", myCol[3])) +
  ylab(" ") +
  xlab("") +
  ggtitle("Body length") +
  coord_cartesian(xlim = c(1.2, NA)) +
  theme(axis.text.x = element_text(
    angle = 30,
    vjust = 1,
    hjust = 1
  ),
  legend.position = "bottom")

Femur_elongation_family <- data %>%
  select(Family, Femur_elongation, Ecological_classification) %>%
  filter(
    Family == "Linyphiidae" |
      Family == "Agelenidae" |
      Family == "Nesticidae" |
      Family == "Leptonetidae" | Family == "Dysderidae"
  ) %>%
  mutate_at("Ecological_classification", as.factor) %>%
  mutate_at("Femur_elongation", as.numeric) %>%
  na.exclude() %>%
  group_by(Family, Ecological_classification) %>%
  filter(n() >= 2) %>%
  ungroup() %>%
  ggplot(
    aes(
      x = Family,
      y = Femur_elongation,
      fill = Ecological_classification,
      colour = Ecological_classification
    )
  ) +
  stat_slab(alpha = .3, colour = NA) +
  stat_pointinterval(position = position_dodge(width = .5, preserve = "single")) +
  scale_fill_manual(values = c("grey20", myCol[3])) +
  scale_colour_manual(values = c("grey20", myCol[3])) +
  ylab("") +
  xlab("") +
  ggtitle("Femur elongation") +
  coord_cartesian(xlim = c(1.2, NA)) +
  theme(axis.text.x = element_text(
    angle = 30,
    vjust = 1,
    hjust = 1
  ),
  legend.position = "bottom")

```

```{r Figure 3,fig.align='center', fig.width=6, fig.height = 4}
Figure_3 <- Body_length_family +
  AME_family +
  PME_family +
  Femur_elongation_family +
  ALE_family +
  PLE_family + plot_layout(ncol = 3, guides = "collect")  +   plot_annotation(tag_levels = 'A') &
  theme(
    plot.tag = element_text(size = 14, face = "bold"),
    legend.position = "bottom",
    legend.text = element_text(size = 14),
    legend.title = element_blank(),
    axis.text.x = element_text(size = 12, hjust = 1),
    axis.text.y = element_text(size = 12)
  ) 
```

```{r, echo=FALSE, fig.width= 6, fig.height=4}
ggsave(plot=Figure_3, filename="Figures/Figure_3.pdf", height=8,width=12,unit="in", device=cairo_pdf)

knitr::include_graphics("Figures/Figure_3.pdf")
```



We have four groups of functional traits :

-   Adaptation
-   hunting strategy
-   Dispersal
-   Morphology

```{r trait similarity}

groups_traits <-
   c(
     rep(1, 8), #Pigment, Eyeless, Eyes_regression, AME_Type
     rep(2, 7), # web and hunting (hunting strategy)
     3, # Dispersal (dispersal)
     4, # Verticality (Verticality)
     rep(5, 2), #Body length and size dimorphism (Morphology)
     rep(1, 2), #Leg Elongation, Femur_elongation (Adaptation)
     5, #Prosoma_shape (morphology)
     2 #Web strategy (hunting strategy)
  )

length(groups_traits) == ncol(trait_m) #check if groups have same length()

## DO NOT RUN

#  fdist <- gawdis(data.frame(trait_m %>% select(-Eye_reduction_ratio)),
#                  groups = groups_traits,
#                  w.type = "optimized",
#                  opti.maxiter = 300,
#                  ord="podani",
#                  groups.weight = TRUE)
# saveRDS(fdist,"functional_distance.rds")

fdist <- readRDS("functional_distance.rds")

#Warning in gawdis(data.frame(trait_m), groups = groups_traits, w.type = "optimized",  :
#  Consider removing traits: Eyeless Tube_web Orb_web Ambush_hunter Active_hunter Food_specialist Dispersal web_strategy, because of unbalanced #distribution.
```

The warning above is due to the distribution on unbalanced traits. In caves, there is a strong filtering effect toward the selection of specific hunting strategies, thereby the observed unbalance (Cardoso, 2012 Int. J. Speleol.)


```{r trait coordinates}
source("get_position.R")

ord <- cmdscale(fdist)
coordinates <- data.frame(ord)
colnames(coordinates) <- c("PC1", "PC2")

centroid <- coordinates %>% as_tibble() %>%
  add_column(family = data$Family) %>%
  group_by(family) %>%
  summarise(cen.1 = mean(PC1), cen.2 = mean(PC2))
fit <- vegan::envfit(ord, trait_m, na.rm = TRUE)

{
  plot(ord)
  trait_position <- get_position(fit, add = TRUE)
}

trait_pos <- data.frame(trait_position) %>%
  rownames_to_column("Trait") %>%
  mutate_at(
    "Trait",
    .funs = forcats::fct_recode,
    "Eyes regression" = "Eyes_regression",
    "Eye reduction ratio" = "Eye_reduction_ratio",
    "Tube web" = "Tube_web",
    "Sheet web" = "Sheet_web",
    "Space web" = "Space_web",
    "Orb web" = "Orb_web",
    "Ambush hunter" = "Ambush_hunter",
    "Active hunter" = "Active_hunter",
    "Diet" = "Food_specialist",
    "Size dimorphism" = "Sexual_Size_Dimorphism",
    "Body size" = "Body_length_avg",
    "Leg elongation" = "Leg_elongation",
    "Femur elongation" = "Femur_elongation",
    "Prosoma shape" = "Prosoma_shape",
    "Pigm.(F)" = "PigmentFully",
    "Pigm.(V)" = "PigmentVariable",
    "Pigm.(P)" = "PigmentPartly",
    "Depigm." = "PigmentDepigmented",
    "Soil" = "VerticalitySoil",
    "Wall" =  "VerticalityWall",
    "Soil+Wall" = "VerticalitySoil + Wall"
  ) %>%
  filter(
    Trait != c(
      "AME_typeAbsent_Adaptation",
      "AME_typeAbsent_Ontology",
      "AME_typePresent"
    )
  )
            
```

# Figure 4 

```{r trait space, message=FALSE, warning=FALSE, fig.align="center"}

theme_set(theme_minimal()) #Setting the theme

plot_space_trait <-  ggplot(data = coordinates, aes(PC1, PC2)) +
  stat_density_2d(
    aes(fill = ..level..),
    geom = "polygon",
    colour = NA,
    alpha = .5,
    h = .25
  ) +
  geom_hline(aes(yintercept = 0), linetype = 3, colour = "gray70") +
  geom_vline(aes(xintercept = 0), linetype = 3, colour = "gray70") +
  geom_point(shape = 19,
             size = .5,
             colour = "black") +
  scale_fill_gradientn(colours = rev(myCol)) +
  theme(
    panel.background = element_rect(
      fill = NA,
      colour = "black",
      size = 1,
      linetype = "solid"
    ),
    panel.grid = element_blank(),
    legend.position = "none"
  ) +
  labs(x = "PCoA 1 (43%)", y = "PCoA 2 (35%)") +
  ylim(-.46, .36) + xlim(-.46, .36) +
  coord_fixed()

library(png)
library(grid)

# LOAD SILLOUETES

#Pholcidae
img <- readPNG("Silhouette/Pholcidae.png")
pholcidae <- rasterGrob(img, interpolate = TRUE)
pholcidae$width <- unit(.6, "npc")
pholcidae$height <- unit(.6, "npc")

#Dysderidae
img <- readPNG("Silhouette/Dysderidae.png")
dysderidae <- rasterGrob(img, interpolate = TRUE)
dysderidae$width <- unit(.6, "npc")
dysderidae$height <- unit(.6, "npc")

#Nesticidae
img <- readPNG("Silhouette/Nesticidae.png")
nesticidae <- rasterGrob(img, interpolate = TRUE)
nesticidae$width <- unit(.6, "npc")
nesticidae$height <- unit(.6, "npc")

#Leptonetidae
img <- readPNG("Silhouette/Leptonetidae.png")
leptonetidae <- rasterGrob(img, interpolate = TRUE)
leptonetidae$width <- unit(.6, "npc")
leptonetidae$height <- unit(.6, "npc")

#Symphytognathidae
img <- readPNG("Silhouette/Symphytognathidae.png")
symphytognathidae <- rasterGrob(img, interpolate = TRUE)
symphytognathidae$width <- unit(.6, "npc")
symphytognathidae$height <- unit(.6, "npc")

plot_families <-
  ggplot(coordinates, aes(PC1, PC2)) +
  stat_density_2d(
    aes(fill = ..level..),
    geom = "polygon",
    colour = NA,
    alpha = .5,
    h = .25
  ) +
  geom_hline(aes(yintercept = 0), linetype = 3, colour = "gray70") +
  geom_vline(aes(xintercept = 0), linetype = 3, colour = "gray70") +
  geom_point(
    data = centroid,
    aes(x = cen.1, y = cen.2),
    shape = 21,
    fill = "white",
    size = 2.5
  ) +
  geom_point(
    data = centroid,
    aes(x = cen.1, y = cen.2),
    shape = 19,
    colour = "black",
    size = 1
  ) +
  annotation_custom(
    pholcidae,
    xmin = -.25,
    xmax = 0,
    ymin = .2,
    ymax = .4
  ) +
  annotation_custom(
    nesticidae,
    xmin = -.15,
    xmax = 0.05,
    ymin = .08,
    ymax = .2
  ) +
  annotation_custom(
    dysderidae,
    xmin = -.25,
    xmax = 0,
    ymin = -.15,
    ymax = -.4
  ) +
  annotation_custom(
    leptonetidae,
    xmin = .15,
    xmax = .37,
    ymin = 0,
    ymax = -.1
  ) +
  annotation_custom(
    symphytognathidae,
    xmin = .05,
    xmax = .15,
    ymin = -0.31,
    ymax = -.38
  ) +
  scale_fill_gradientn(colours = rev(myCol)) +
  ggrepel::geom_text_repel(data = centroid,
                           aes(x = cen.1,
                               y = cen.2,
                               label = family)) +
  theme(
    panel.background = element_rect(
      fill = NA,
      colour = "black",
      size = 1,
      linetype = "solid"
    ),
    panel.grid = element_blank(),
    legend.position = "none"
  )  +
  labs(x = "PCoA 1 (43%)", y = "PCoA 2 (35%)") +
  ylim(-.46, .36) + xlim(-.46, .36) +
  coord_fixed()

plot_traits <-   ggplot(coordinates, aes(PC1, PC2)) +
  stat_density_2d(
    aes(fill = ..level..),
    geom = "polygon",
    colour = NA,
    alpha = .5,
    h = .25
  ) +
  geom_hline(aes(yintercept = 0), linetype = 3, colour = "gray70") +
  geom_vline(aes(xintercept = 0), linetype = 3, colour = "gray70") +
  geom_point(
    data = trait_pos,
    aes(x = Dim1, y = Dim2),
    shape = 21,
    fill = "white",
    size = 2.5
  ) +
  geom_point(
    data = trait_pos,
    aes(x = Dim1, y = Dim2),
    shape = 19,
    colour = "black",
    size = 1
  ) +
  scale_fill_gradientn(colours = rev(myCol)) +
  ggrepel::geom_text_repel(data = trait_pos, aes(x = Dim1, y = Dim2, label = Trait)) +
  theme(
    panel.background = element_rect(
      fill = NA,
      colour = "black",
      size = 1,
      linetype = "solid"
    ),
    panel.grid = element_blank(),
    legend.position = "none"
  )  +
  labs(x = "PCoA 1 (43%)", y = "PCoA 2 (35%)") +
  ylim(-.46, .36) + xlim(-.46, .36) +
  coord_fixed()

plot_bs <-  trait  %>%
  ggplot(aes(x = expm1(Body_length_avg))) +
  geom_density(fill = myCol[3],
               alpha = 1,
               colour = "black") +
  labs(title = "Body Size (mm)", x = NULL, y = "Density") +
  theme(
    plot.background = element_blank(),
    panel.grid = element_blank(),
    axis.line.y = element_line(),
    axis.line.x = element_line(),
    rect = element_blank(),
    axis.title.y = element_text(size = 10, colour = "black"),
    axis.text.x = element_text(size = 10, colour = "black")
  )

plot_disp <-  trait %>%
  ggplot(aes(x = as.factor(Dispersal), fill = as.factor(Dispersal))) +
  geom_bar(stat = "count",
           colour = "black",
           alpha = 1) +
  scale_fill_manual(values = c("grey20", myCol[3])) +
  theme(
    legend.position = "none",
    plot.background = element_blank(),
    panel.grid = element_blank(),
    axis.line.y = element_line(),
    axis.line.x = element_line(),
    rect = element_blank(),
    axis.title.y = element_text(size = 10, colour = "black"),
    axis.text.x = element_text(size = 10, colour = "black")
  ) + labs(title = "Dispersal", x = NULL, y = "Number of species") +
  scale_x_discrete(labels = c("No", "Yes"))

plot_FE <-
  trait %>%
  ggplot(aes(x = expm1(Femur_elongation))) +
  geom_density(fill = "gray20",
               alpha = 1,
               colour = "black") +
  labs(title = "Femur elongation (ratio)", x = "", y = "Density") +
  theme(
    plot.background = element_blank(),
    panel.grid = element_blank(),
    axis.line.y = element_line(),
    axis.line.x = element_line(),
    rect = element_blank(),
    axis.title.y = element_text(size = 10, colour = "black"),
    axis.text.x = element_text(size = 10, colour = "black")
  )

plot_SW <-
  trait %>%
  ggplot(aes(x = as.factor(Space_web), fill = as.factor(Space_web))) +
  geom_bar(stat = "count",
           colour = "black",
           alpha = 1) +
  scale_fill_manual(values = c("grey20", myCol[3])) +
  theme(
    legend.position = "none",
    plot.background = element_blank(),
    panel.grid = element_blank(),
    axis.line.y = element_line(),
    axis.line.x = element_line(),
    rect = element_blank(),
    axis.title.y = element_text(size = 10, colour = "black"),
    axis.text.x = element_text(size = 10, colour = "black")
  ) + labs(title = "Space web", x = NULL, y = "Number of species") +
  scale_x_discrete(labels = c("No", "Yes"))
```

```{r Figure 4 , message = FALSE, warning = FALSE, fig.width = 7, fig.height =5}
panel_d <- (plot_bs + plot_disp) / (plot_SW + plot_FE)
panel_d <- ggpubr::as_ggplot(patchworkGrob(panel_d))
Figure_4 <- plot_space_trait + plot_families + plot_traits + panel_d +
plot_annotation(tag_levels = 'A') &
theme(plot.tag = element_text(size = 12, face = "bold"))
```

```{r, echo=FALSE}
ggsave(
plot = Figure_4,
filename = "Figures/Figure_4.pdf",
device = cairo_pdf,
width = 14,
height = 10,
units = "in"
)

knitr::include_graphics("Figures/Figure_4.pdf")
```
